Check Coverage

### 2020-10-12 analysis/calc_fd.Rmd

@@

  fd_out <- as_tibble(dbFD_joggle(trait_mat, select(species_mat, -year), w.abun = TRUE, ...))[,1:8] %>%
    cbind(years, .) %>%
    mutate(plot_id = unlist(filter_plot), trait_count = dim(trait_mat)[2])
    write_tsv(fd_out, paste0(here::here("data"), "/fd_output/", filter_plot, "_fd.tsv"))

@@

Read data back in, excluding sites/plots as they become a problem:
```{r}
files <-  dir(here::here("data", "fd_output"), "*.tsv")

>>>>

source(here::here("R", "dbFD_mine.R"))

@@

  fd_data <- dbFD_mine(trait_mat, select(species_mat, -year), w.abun = TRUE, ...)
  fd_out <- as_tibble(fd_data$fd_met)[,1:8] %>%
    cbind(years, .) %>%
    mutate(plot_id = unlist(filter_plot), trait_count = dim(trait_mat)[2])

    write_tsv(fd_out, paste0(here::here("data"), "/fd_output/", filter_plot, "_fd.tsv"))
    write_tsv(fd_data$pca_traits, paste0(here::here("data"), "/fd_output/", filter_plot, "_traits.tsv"))

@@

Read data back in, excluding sites/plots as they become a problem:
```{r}
files <-  dir(here::here("data", "fd_output"), "*_fd.tsv")

### 2020-10-12 analysis/merge_data.Rmd
Create one weight column that is either abundance or biomass

biotime_traits <- comp_biotime_traits %>%
  #get studies with appropriate coverage and drop observations that we don't have trait data for
  filter(study_id %in% inc_coverage$study_id, !is.na(scientificName)) %>% 
  mutate(plot_id = paste0(study_id, plot))
```

>>>>

biotime_traits <- comp_biotime_traits %>%
  #get studies with appropriate coverage and drop observations that we don't have trait data for, and unlabeled non-id'd species
  filter(study_id %in% inc_coverage$study_id, !is.na(scientificName), !is.na(plot)) %>% 
  mutate(plot_id = paste0(study_id, plot)) %>%
  group_by(plot_id, year) %>%
  filter(n_distinct(id) > 4) %>%
  group_by(plot_id) %>%
  filter(n_distinct(year) > 4) %>%
  ungroup()
```

Create one weight column 
```{r}
biotime_traits <- biotime_traits %>%
  mutate(weight = case_when(
    year_abun != 0 ~ year_abun,
    TRUE ~ year_biomass
  )) %>%
  select(-c(year_abun, year_biomass))
```
